The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2017-08-10 paper/ms.tex
Updates to paper

\author{J. A. ZuHone\altaffilmark{1}, K. Kowalik\altaffilmark{2}, E. \"{O}hman\altaffilmark{3}, E. Lau\altaffilmark{3}}

\altaffiltext{1}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA}
\altaffiltext{2}{National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, 1205 W. Clark St., MC-257, Urbana, IL 61801, USA}
\altaffiltext{3}{Department of Physics, Yale University, New Haven, CT 06520, USA}

@@

The astrophysical literature is replete with simulations of galaxy cluster mergers, from binary merger simulations \citep[e.g.][]{ric01,poo06,zuh11,don13} to studies of mergers in cosmological simulations \citep[e.g.][]{vaz09,ski13,yu15}. These simulations have often attempted to make predictions for what may be observed in a number of wavebands and made direct comparisons to observed merging systems. However, comparing the results of simulations of cluster mergers to these systems is often not straighforward; at what stage are we viewing the merger, and along what line of sight? To make matters more complicated, different combinations of merger epoch and line of sight can produce qualitatively similar projections of cluster emission, making it more difficult to use observations to determine these parameters and distinguish between different theoretical models.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{halo_page.eps}
\caption{A portion of a ``halo page,'' showing the details of the halo information and the slice data for this particular halo. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/00086.html}.}
\end{center}
\end{figure*}

@@

We {\bf have presented} the ``Galaxy Cluster Merger Catalog,'' a website designed to provide a simple yet powerful interface to accessing mock observations of {\bf galaxy clusters}. {\bf The catalog} includes a suite of mock observations from a number of binary cluster merger {\bf and cosmological} simulations, with different initial conditions and/or input physics. In particular, the catalog provides a number of X-ray and S-Z synthetic observations as well as mock galaxy catalogs {\bf for some simulations}. Projections of the observables have been taken along a number of lines of sight through the simulation box, and at a large number of epochs for each simulation so that the merger history is well-sampled in time. {\bf The catalog interface is designed to facilitate quick and straightforward comparisions between the different simulations.} This large parameter space of cluster mergers will be useful when comparing with observed cluster mergers in a number of wavebands.

@@

{\bf Comparisons of data from the catalog to current observations have already been made to useful effect by \citet{wal17} and Douglass et al. 2017, in preparation.} It is our hope that the catalog will {\bf continue to provide} a useful resource for researchers studying galaxy cluster mergers from both the perspective of current observations as well as making predictions for future missions.

>>>>

\author{J. A. ZuHone\altaffilmark{1}, K. Kowalik\altaffilmark{2}, E. \"{O}hman\altaffilmark{3}, E. Lau\altaffilmark{3,4}, D. Nagai\altaffilmark{3,4,5}}

\altaffiltext{1}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA}
\altaffiltext{2}{National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, 1205 W. Clark St., MC-257, Urbana, IL 61801, USA}
\altaffiltext{3}{Department of Physics, Yale University, New Haven, CT 06520, USA}
\altaffiltext{4}{Yale Center for Astronomy and Astrophysics, Yale University, New Haven, CT 06520, USA}
\altaffiltext{5}{Department of Astronomy, Yale University, New Haven, CT 06520, USA}

@@

The astrophysical literature is replete with simulations of galaxy cluster mergers, from binary merger simulations \citep[e.g.][]{ric01,poo06,zuh11a,don13} to studies of mergers in cosmological simulations \citep[e.g.][]{vaz09,ski13,yu15}. These simulations have often attempted to make predictions for what may be observed in a number of wavebands and made direct comparisons to observed merging systems. However, comparing the results of simulations of cluster mergers to these systems is often not straighforward; at what stage are we viewing the merger, and along what line of sight? To make matters more complicated, different combinations of merger epoch and line of sight can produce qualitatively similar projections of cluster emission, making it more difficult to use observations to determine these parameters and distinguish between different theoretical models.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{halo_page.eps}
\caption{A portion of a ``halo page,'' showing the details of the halo information and the slice data for this particular halo. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/00086.html}.}
\end{center}
\end{figure*}

@@

We {\bf have presented} the ``Galaxy Cluster Merger Catalog,'' a website designed to provide a simple yet powerful interface to accessing mock observations of {\bf galaxy clusters}. {\bf The catalog} includes a suite of mock observations from a number of binary cluster merger {\bf and cosmological} simulations, with different initial conditions and/or input physics. In particular, the catalog provides a number of X-ray and S-Z synthetic observations as well as mock galaxy catalogs {\bf for some simulations}. Projections of the observables have been taken along a number of lines of sight through the simulation box, and at a large number of epochs for each simulation so that the merger history is well-sampled in time. {\bf The catalog interface is designed to facilitate quick and straightforward comparisons between the different simulations.} This large parameter space of cluster mergers will be useful when comparing with observed cluster mergers in a number of wavebands.

@@

{\bf Comparisons of data from the catalog to current observations have already been made to useful effect by \citet{wal17} and Douglass et al. 2017, in preparation. The catalog is also being explored as an avenue for further simulation investigations as well. The simulated X-ray images from several of the simulations are currently being analyzed with edge-detection techniques to determine if such an approach can reveal differences in the X-ray surface brightness distribution produced by varying the plasma physics of the ICM, including the strength of the magnetic field and viscosity (Bellomi et al., in preparation). Another area of research that is being explored by the authors of this work involves extracting cluster merger parameters from mergers in cosmological simulations and using them as inputs for idealized simulations, applying different prescriptions for the physics of the ICM in different simulations. This will be particularly useful from the perspective of determining the effect of varying the ICM physics on the velocity field of merging clusters, which will be an area of intense research with the advent of X-ray observatories carrying instruments which can measure such motions. The fruits of this research will eventually become part of the catalog as well.} It is our hope that the catalog will {\bf continue to provide} a useful resource for researchers studying galaxy cluster mergers from both the perspective of current observations as well as making predictions for future missions.
